### 2020-04-09 0_abstract.tex
Trim abstract down to the word limit for SC.

@@

We conduct a comprehensive study with implementations of Task Bench in
15 programming systems on up to 256 Haswell nodes of the Cori
supercomputer. We introduce a novel metric, \emph{minimum effective task
  granularity} to study the baseline runtime overhead of each
system. We show that when running at scale, 100~\textmu{}s is the
smallest granularity that even the most efficient systems can reliably
support with current technologies. We also study each system's
scalability, ability to hide communication and mitigate load
imbalance.
\end{abstract}

>>>>

% 150 words

@@

We conduct a comprehensive study with
15 programming systems on up to 256 Haswell nodes of the Cori
supercomputer. We introduce a novel metric, \emph{minimum effective task
  granularity} to study the baseline runtime overhead of each
system. Running at scale, 100~\textmu{}s is the
smallest granularity that any system can reliably
support with current technologies. We also study each system's
scalability, ability to hide communication and mitigate load
imbalance.
\end{abstract}
